%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Frontend Developer} % Job title
    {TECHVERX} % Organization
    {Lahore, Pakistan} % Location
    {Jan. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated with stakeholders during development processes to confirm creative proposals and design best practices.}
        \item {Handled design, development, deployment and maintenance of integration processes with \textbf{React} and \textbf{Redux} as \textbf{state managment}.}
        \item {Managed version control with \textbf{Git} and \textbf{Github}.Used \textbf{JIRA} to manage project timeline for updates and identifing issues.}
        \item {Planned website development, converting mock ups into usable web presence with \textbf{HTML5}, \textbf{CSS3}, \textbf{jQuery} and \textbf{SASS}.}
        \item {Implemented websites, mobile applications, and landing pages from concept through deployment.}
        \item {Converted design assets into \textbf{responsive} component-based HTML5, CSS3, JavaScript ,\textbf{Bootstrap}, \textbf{ReactJs} and \textbf{Redux}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Frontend/WordPress Developer} % Job title
    {UNIVERSAL SOLZ.} % Organization
    {Lahore, Pakistan} % Location
    {Aug. 2020 - Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created and updated re-usable code libraries to streamline \textbf{WordPress} development cycle.}
        \item {Improved and expanded project platforms using JavaScript to develop rich User Interfaces.}
        \item {Developed an Custom Post to use as projects in dashboard which is gettingg content from \textbf{ACF(advanced custom field)}.}
        \item {Created UI template for the \textbf{Custom Post Types} and \textbf{ACF}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Frontend Developer} % Job title
    {FIWD INC.} % Organization
    {Lahore, Pakistan} % Location
    {Jan. 2020 - Jul. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and made \textbf{responsive} layouts to meet usability and performance requirements.}
        \item {Converted design assets into \textbf{responsive} component-based \textbf{HTML5}, \textbf{CSS3}, \textbf{JavaScript} ,\textbf{Bootstrap}, \textbf{SASS} and \textbf{LESS}.}
        \item {Developed an layout for a project with \textbf{Tailwindcss3}.}
        \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer Intern} % Job title
    {WEBSOL} % Organization
    {Lahore, Pakistan} % Location
    {November. 2019 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed \textbf{API server} which is communicating with client and used \textbf{Heroku} for deployment.}
        \item {Won the \textbf{2nd prize in final evaluation}.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
